ohbm_results

### 2023-11-28 ohbm_results.Rmd
finalize ohbm plots, adding EDA for next-steps

```{r}
cent.diffs.v.plot <- cent_err.p %>%
  mutate(mean = mean*100) %>% #for visuals
  ggplot() +
  geom_violin(aes(x=dataset, y=mean, fill=permutation))
ggsave(filename="figs/centile_violin.png", cent.diffs.v.plot)
```

@@

```{r}
fwrite(z_t.tests.p, file="ukb_permute/z_t.tests.csv")
```

@@

    # Add a "Source_File" column with the file name
    data <- data %>%
      mutate(Source_File = as.factor(basename(file)),
             perm = as.factor(x)) %>%
      mutate(dataset = gsub("_data|_variance.csv|perm-|[0-9]|-", "", Source_File),
             sex_standard = sex_effect/f.var)

@@

perm_var <- mclapply(n_perm_list, get.var, mc.preschedule = FALSE)
```

@@

```{r}
#get summary df for p vals, plotting
sigma.sex.df <- fread("ukb_basic/gamlss_summary.csv", stringsAsFactors = TRUE) %>%
  dplyr::select(-V1) %>%
  mutate(dataset = gsub("-data", "", dataset),
         dataset = gsub("-", "_", dataset),
         dataset = gsub("_simsites", "", dataset)) %>% #clean up dataset naming
  mutate(dataset = factor(dataset, levels = unique(dataset), ordered = FALSE)) %>%
  mutate(dataset = relevel(dataset, ref= "ukb_CN")) %>%
  dplyr::filter(parameter == "sigma" & term == "sexMale") %>%
  dplyr::select(mod_name, pheno, dataset, pheno_cat, label, sig.sum_bf.corr)

```{r}
plot_male_var <- function(df) {
permutation <- unique(df[["perm"]])

sex_effect_plot <- df %>%
  mutate(sex_standard = case_when(isTRUE(sig.drop_bf.corr)~ sex_standard,
                                   isFALSE(sig.drop_bf.corr) ~ NA)) %>% #only significant effects
  ggplot() +
  geom_bar(aes(x=pheno, y=sex_standard, fill=dataset)) +
  facet_wrap(~pheno_cat) +
  ggtitle(paste("Standardized effect of male sex on variance:", permutation))

  ggsave(paste0("figs/male_variance_ohbm", permutation, ".jpeg", sex_effect_plot)
  print(sex_effect_plot)
}

#mclapply

```

>>>>

```{r}
cent.diffs.v.plot <- cent_err.p %>%
  mutate(mean = mean*100) %>% #for visuals
  ggplot() +
  geom_violin(aes(x=dataset, y=mean, fill=permutation)) +
  labs(y= "Magnitude Centile Error", x = "ComBat Configurations") +
  ggtitle("Within-subject mean magnitude of error in centile scores across ComBat \nconfigurations replicated 10x")
ggsave(filename="figs/centile_violin.png", cent.diffs.v.plot)
```

@@

```{r}
fwrite(z_t.tests.p, file="ukb_perm_csvs/z_t.tests.csv")
```

```{r}
z_t.tests.p %>%
  group_by(comp) %>%
  dplyr::summarize(n_sig_min=min(n_sig_regions),
            n_sig_max = max(n_sig_regions),
            n_sig_mean = mean(n_sig_regions))
```

@@

    # Add a "Source_File" column with the file name
    data <- data %>%
      mutate(Source_File = as.factor(basename(file)),
             perm = as.factor(x)) %>%
      mutate(dataset = gsub("_data|_variance.csv|perm-|[0-9]|-", "", Source_File),
             sex_standard = sex_effect/f.var,
             pheno = as.character(pheno))

@@

perm_var <- mclapply(n_perm_list, get.var, mc.preschedule = FALSE)
perm_var.all <- bind_rows(perm_var, .id = "column_label")
```

@@

```{r}
#get summary df for p vals, plotting
sigma.sex.df <- fread("ukb_perm_csvs/sex_summary.csv", stringsAsFactors = TRUE) %>%
  dplyr::select(-V1) %>%
  mutate(perm = gsub("ukb-CN-data-agefilt-|-raw|-cf|.lm|.gam|.gamlss|-data", "", dataset),
         dataset = gsub("-data", "", dataset),
         dataset = gsub("simsites|ukb-CN-agefilt-|perm-|[0-9]", "", dataset),
         dataset = gsub("-", "", dataset),
         #dataset = as.character(dataset),
         pheno = as.character(pheno)) %>%
  mutate(dataset = factor(dataset, levels = unique(dataset), ordered = FALSE),
         perm = factor(perm, levels = unique(perm), ordered=FALSE)) %>%
  #mutate(dataset = relevel(dataset, ref= "raw")) %>%
  dplyr::filter(parameter == "sigma" & term == "sexMale") %>%
  dplyr::select(mod_name, pheno, dataset, pheno_cat, label, sig.sum_bf.corr, perm, sig.drop_bf.corr)

perm_var_info <- inner_join(perm_var.all, sigma.sex.df)
```

```{r}
  sex_effect_plot <- perm_var_info %>%
    mutate(sex_standard = case_when(sig.drop_bf.corr == TRUE ~ sex_standard,
                                    sig.drop_bf.corr == FALSE ~ 0)) %>% #only significant effects
    ggplot() +
    geom_col(aes(x=pheno, y=sex_standard, fill=dataset)) +
    facet_wrap(~perm, ncol=5) +
    ggtitle(paste("Standardized effect of male sex on variance:", permutation)) +
    theme(axis.text.x = element_blank())

    ggsave(paste0("figs/male_variance_perms.jpeg"), sex_effect_plot)
    print(sex_effect_plot)
```
